Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-07 manuscript.tex
knit

We identified five key features of long-form audio methods that should be replicated in analogous studies of motor behavior. First, wearable audio recorders are \emph{mobile}. Measurement is not limited to a particular room because the recording device travels with the participant. Data are recorded to onboard device memory, so participants do not need to be in range of a receiver. Second, wearable audio recording is \emph{unobtrusive}. Participants' reactivity to observation, such as from a video camera, may influence behavior. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA® device (Bergelson, Amatuni, et al., 2019). Third and fourth, recordings capture \emph{real-time data} over a \emph{full day}. The ability to record real-time data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual (e.g., Wass et al., 2022). Full-day recordings are essential for capturing experiences across the heterogeniety of daily routines that moderate behavior (e.g., play, feeding, errands) (Kadooka et al., 2021, April). ``Burstiness'' of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent (Barbaro \& Fausey, 2022; Warlaumont et al., 2021). Fifth, \emph{automatic classification} means that the approach can scale to analyze large numbers of participants over long recordings without the bottleneck of manual annotation/transcription. Automatic classification can only replace human annotation if it is sufficiently accurate and unbiased. An independent assessment of the LENA® algorithms found mixed results about the accuracy of different outcomes. For example, correlations between human transcribed counts of adult words and child vocalizations against LENA®'s automatic counts were strong, \emph{r} = .698 and \emph{r} = .649, respectively (Cristia et al., 2020). However, poor agreement was found for other metrics, such as the number of ``conversational turns'' between the child and communicative partners and the identification of male speakers.

@@

\caption{Example Timeline Caption.}\label{fig:exemplartimeline}
\end{figure}

\hypertarget{body-position-annotation}{%
\subsection{Body position annotation}\label{body-position-annotation}}

@@

@@

>>>>

We identified five key features of long-form audio methods that should be replicated in analogous studies of motor behavior. First, wearable audio recorders are \emph{mobile}. Measurement is not limited to a particular room because the recording device travels with the participant. Data are recorded to onboard device memory, so participants do not need to be in range of a receiver. Second, wearable audio recording is \emph{unobtrusive}. Participants' reactivity to observation, such as from a video camera, may influence behavior. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA® device (Bergelson, Amatuni, et al., 2019). Third and fourth, recordings capture \emph{real-time data} over a \emph{full day}. The ability to record real-time data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual (e.g., Wass et al., 2022). Full-day recordings are essential for capturing experiences across the heterogeniety of daily routines that moderate behavior (e.g., play, feeding, errands) (Kadooka et al., 2021, April; Tamis-LeMonda et al., 2018). ``Burstiness'' of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent (Barbaro \& Fausey, 2022; Warlaumont et al., 2021). Fifth, \emph{automatic classification} means that the approach can scale to analyze large numbers of participants over long recordings without the bottleneck of manual annotation/transcription. Automatic classification can only replace human annotation if it is sufficiently accurate and unbiased. An independent assessment of the LENA® algorithms found mixed results about the accuracy of different outcomes. For example, correlations between human transcribed counts of adult words and child vocalizations against LENA®'s automatic counts were strong, \emph{r} = .698 and \emph{r} = .649, respectively (Cristia et al., 2020). However, poor agreement was found for other metrics, such as the number of ``conversational turns'' between the child and communicative partners and the identification of male speakers.

@@

\caption{Example Timeline Caption.}\label{fig:exemplar-timeline}
\end{figure}

Figure \ref{fig:exemplar-timeline}) shows an exemplar timeline of the entire procedure and recording periods for a single participant. On the day of the visit, a researcher arrived at the participant's home in the morning between and prepared all the equipment at the doorstep. In order to synchronize all three recording devices, the researcher began by first turning on the video camera and the LENA audio device (the IMUs were already configured and placed at arrival because they required a proprietary sensor dock to begin recording in the laboratory). To create an easily recognizable synchronization point between the video recording and IMU data, the researcher dropped or struck the leggings (containing the IMUs) on a surface in view of the camera, as in (Franchak et al., 2021). All the equipment---once recording and with synchronization information recorded---was placed inside a large bucket and left outside the family's front door.

The researcher then called the caregiver on the phone and walked them through a set of procedures needed to properly set up the equipment and record video for classifier training and testing. At the start of this ``guided call'', the caregiver was instructed to place the camera in an area that captured the majority of the room. Next, they were asked to put the pair of leggings and shirt on their infant, with the researcher providing guidance about how to correctly orient the garments.

Afterwards, the researcher asked the caregiver to complete a number of guided activities with their infant. Within view of the camera, the caregiver was asked to place their infant in several different positions: lying supine, lying prone, sitting on the floor, standing upright, held by the caregiver while the caregiver walked back and forth, crawling, walking, and sitting in a restrained seat (e.g., high chair). Depending on the infants' age and motor skill level, the positions could be done independently or were completed with assistance from the caregiver. The researcher kept time to ensure at least 1 minute of behavior for each activity. Once completed, the caregiver was then instructed to play with their infant for 10 minutes within view of the camera to collect additional training data with the infant in positions that would be typical of play.

Afterwards, they were to go about their day as usual with the infant wearing the sensor garment until their bedtime, only taking off the sensor for naps, baths, and diaper changes. The caregiver logged the times the sensors were removed (blank areas in the timeline in Figure \ref{fig:exemplar-timeline})) or the child took a nap (gray areas in the timeline in Figure \ref{fig:exemplar-timeline})) so that those times could be excluded from analysis. The following day a researcher picked up the equipment, verified the paperwork was signed, and compensated the participant.

Because the camera only had the battery life to record for \textasciitilde3 hours (divided into two 90-minute video files), this divided the day into different periods for analysis. As seen in the bottom of Figure \ref{fig:exemplar-timeline}), the \emph{video period} comprised the first three hours of recording starting from the researcher's arrival when they turned on the camera. The first 90-minute video file, termed the \emph{proximal comparison}, contained the activities during the guided call followed by a period of infants and caregivers resuming their normal activities. Because this video contained the synchronization point, the data in this period had temporal synchrony between IMU and video data that contained errors of no more than 30-60 ms (1-2 video frames). When the first video file ended, a second video file was recorded, termed the \emph{distal comparison}. This video recorded the next 90 minutes of natural activity. However, because there was a variable gap of \textasciitilde40 s between the two videos, temporal synchrony in the distal comparison video was approximate containing offsets of \textasciitilde{} 5-10 s.

\hypertarget{body-position-annotation}{%
\subsection{Body Position Annotation}\label{body-position-annotation}}

The proximal and distal comparison videos for each participant were annotated by trained human coders to identify infant \emph{body position} into one of 5 mutually-exclusive categories: supine, prone, sitting, upright, or held by caregiver. All coding was done using Datavyu software (datavyu.org).

Supine was coded when the infant was lying on their back or was reclined up to a 45 degrees angle. Supine was also coded in the rare cases when the infant was laying on their side. Prone was coded when the infant was lying on their stomach, was on all fours in a downward dog position, or was crawling. We scored sitting to include any form of the following seated positions: 1) infants sat with their buttocks on a surface, such as on the floor or a caregiver's lap, 2) infant was in a kneeling-sit position, in which their knees were on the ground with their legs tucked underneath the buttocks, and 3) infant was in a seating device, such as a high chair, that kept the torso oriented perpendicular to the ground (a reclined position, such as in a young infant's car seat, would be counted as supine). Upright was coded when the infant was standing on the ground with two feet or walking (regardless of whether infants' balance was assisted by a caregiver or with their hands holding onto something for support). When an infant was carried by a caregiver, held was coded. However, when the caregiver was sitting with the infant in their lap the infant's body position was coded as if the caregiver was a surface (e.g., if the infant was sitting on the caregiver's lap this was coded as sitting). Times during the video when the infant was out of view were excluded. Periods when the leggings were being adjusted or taken off the infant were also excluded, as were transitions between body positions.

A primary coder completed annotation for the full length of the video, while an independent reliability coder completed annotation for the first thirty minutes of each video. Interrater reliability was based on the proportion of video frames that the two coders chose the same body position code. Overall agreement averaged XX.X\% across video files, ranging from XX-XX. Cohen's \emph{kappa} ranged from XX-XX across files, with a mean of XX.

@@

\hypertarget{data-sharing-and-transparency}{%
\subsection{Data Sharing and Transparency}\label{data-sharing-and-transparency}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Tamis-LeMondaCustode2018}{}}%
Tamis-LeMonda, C. S., Custode, S., Kuchirko, Y., Escobar, K., \& Lo, T. (2018). Routine language: Speech directed to infants during home activities. \emph{Child Development}, \emph{90}(6), 2135--2152. \url{https://doi.org/10.1111/cdev.13089}
